Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
related work

\subsection{Usability Work on Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

\subsection{Usable Security and User Behavior} %%%%%%
% Okay, this is a mess. Last brain dump before sleep. 
\indent \indent {\color {red} 
The work that started usable security, using a cognitive walkthough to expose usability issues
in PGP ~\cite{whitten1999johnny}. The authors give suggestions for better usability, such as 
aligning words to pictures, etc.

 Work which shows that people are willing to give up privacy for instant gratification with respect to 
 e-commerce, showing that participants' motivations are not aligned for preserving privacy, but to 
 complete the task at hand. ~\cite{acquisti2004privacy}. Talk about how censorship might be different
 because people need to actually configure to succeed.

 People care about how easy something is to use when picking software ~\cite{}.

 infrastructure is highly distributed, with the bundle of
tools in one single installer (below is the screenshot of
the Vidalia control panel, which runs on many different
platforms), making the technology accessible to average
users BUt people don't care.

 users should not only look at the technical angle of their
approach, but should also be aware of frequent attempts
to infiltrate or otherwise identify social networks of
people with dissenting opinions, even when they are
only partially operating online.

you might want to choose a system based on the usability of others 
~\cite{dingledine2006anonymity}.

  }

@@

\section{UX sprint} %%%%%%
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to licit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.

>>>>

\subsection{Usability for Security Software}
\indent \indent 
We evaluate the usability of the configuration window's interface. Generally, usability 
refers to the learnability, efficiency, memorability, error rate/recoverability, and satisfaction
during use. To achieve these goals, the HCI community has established heuristics for user
interface design: visibility of the system status, using familiar
language, preventing errors, having consistent visuals, flexibility and efficiency of use, 
error recovery, and leveraging recognition over memorization ~\cite{nielsen199510}. Note
that these are not specific usability guidelines, but heuristics.

Usability has sligtly different meanings depending on the context. Some emphasize
learnability, flexibility, and ease of user. In a security context, the priorities are whatever is 
required for the security to be used effectively. As stated by Whitten \etal, a security software is 
usable if people who are expected to use it are reliably made aware of the security tasks to perform, 
are able to figure out how to successfully perform those tasks, do not make dangerous errors, and
are sufficiently comfortable with the software interface ~\cite{whitten1999johnny}. Since usable security 
has user interface design goals than general consumer software, it likewise requires usability evaluation
methods which are suitable to test these properties. Our goals are to test that the Tor Browser, 
communicates an accurate conceptual model of the task to the users as quickly as possible, provide guidance to 
users at the right time, and use warnings and other interactive tools to prevent any mistakes.

\subsection{Usability and Tor}
\indent \indent  Work by Clark \etal to explore ways to simplify the Tor user interface
has led to great usability improvements ~\cite{clark2007usability}.  Clark analyzed the challenges 
of using multiple Tor-related tools including TorPark, Vidalia, FoxyProxy, and TorButton to find that
none are fully satisfactory from a usability perspective. Researchers provide guidelines on 
how to incorporate the best aspects of each tool, while providing a set of guidelines drawn from
usable security and computer human interaction. Key takeaways from this work includes 
finding out that exposure to how Tor works may be difficult for users to understand, and that 
familiar, non-technical language is critical for communication. We plan to draw from Clark's
guidelines as well as other works in usable security and computer human interaction to suggest
any improvements to the Tor Browser.

@@

@@

\section{UX sprint}
\label{sec:pilot}
\indent \indent This pilot was to test-drive an experiment which examines the usability of Tor as an anonymity tool
with respect to a target demographic of users known to use Tor (journalists who have reported in other
countries). We emphasized the targeting of a high-risk user group of Tor and to 
target usability changes aimed at helping those who could not afford to make mistakes. To see 
if those users had any potentially damaging misunderstandings or incomprehensions of Tor, 
we created tasks to licit Tor's non-typical behaviors and ask our participants to
navigate through more advanced settings.
